---
title: "Customer Intelligence"
author: '[Leonard Henriquez](https://github.com/leonard-henriquez/), [Adrien Lequiller](https://github.com/adrienlequiller) & [Eddy Ohayon](https://github.com/Eddoha55)'
date: "`r Sys.Date()`"
output: html_document
always_allow_html: yes
---

# Data preparation

```{r message=FALSE, warning=FALSE, include=FALSE}
# Options
knitr::opts_chunk$set(cache = TRUE, warning=FALSE)
library(mlogit)
library(MASS)
library(ggplot2)
```

Read in the data

```{r}
# all alternatives
x<-read.csv("input/19019700001_conjoint_choice_dat_X.csv")

# choice per display group
y<-read.csv("input/19019700001_conjoint_choice_dat_y.csv")

# demographic information
z<-read.csv("input/19019700001_conjoint_choice_dat_Z.csv")
colnames(z)[2:4] <- c("sex", "age", "perception")
```

Demographic analysis

```{r}
ggplot(z)+aes(sex)+geom_bar() # a bit more female than male
ggplot(z)+aes(age)+geom_bar() # a large majority of people between 18-24
ggplot(z)+aes(perception)+geom_bar() # most of the respondents people have a positive perception
```


Transform the data into long format

```{r}
choicesperquestions<-3

for (i in 1:nrow(y))
{
  y[i,"y"]=(i-1)*choicesperquestions+y[i,"y"]
}

x$choice<-0
for (i in 1:nrow(y))
{
  j=y[i,"y"]
  x[j,"choice"]<-1
}

x$Profile<-NULL
alternative<-1
questioncounter<-1
x$ques<-0
x$alt<-0
lastid<-x[1,1]
for (i in 1:nrow(x))
{
  if(x[i,1]!=lastid)
  {
    lastid=x[i,1]
    questioncounter<-0
  }
  if(alternative<=choicesperquestions)
  {
    x[i,"ques"]<-questioncounter
    x[i,"alt"]<-alternative
    alternative<-alternative+1
  }
  else
  {
    questioncounter<-questioncounter+1
    alternative<-1
    x[i,"ques"]<-questioncounter
    x[i,"alt"]<-alternative
    alternative<-alternative+1
  }
}
x[,"choice"] <- x[,"choice"] == 1

# merge a valid covariate here: in my case sex, age, perception.
x<-merge(x,z,by="ID",all.x=TRUE)
summary(x)
```

Our data x is now in the long format so you can launch the first two solution methods

# Analysis

Let's explore the data to see the choices for each possible alternative
```{r}
# Price
xtabs(choice~price,data=x)

# Brand
xtabs(choice~brand,data=x)

# Type
xtabs(choice~type,data=x)

# Gear
xtabs(choice~gear,data=x)

# Options
xtabs(choice~options,data=x)
```


Creation d'un model multinomial

```{r}
car.mlogit <- mlogit.data(data=x, choice="choice", shape="long", alt.levels=paste("pos",1:3), id.var="ID")
m1<-mlogit(choice ~ 0 + brand + price + type + gear + options, data=car.mlogit)
summary(m1)
```

Analyse:
- Le type de transmission n'a pas d'impact significatif sur le choix d'une voiture
- Marque: pas de diff??rence significative entre Audi et BMW, mais par contre la "willingness to pay"" d'un client pour une Mercedes est plus faible de 26577.99 euros (faire apparaitre le calcul coef(m1)["brandMercedes"]/coef(m1)["price"] ) et pr??ciser quece chiffre refl??te certainement un biais d'??chantillon
- Price: le prix a un impact significatif sur le choix
- Type: pas d'impact que ??a soit une berline ou un SUV, par contre une city_car baisse la willingness to pay de 8613.325 euros (coef(m1)["typecity_car"]/coef(m1)["price"])
- Options: a un impact significatif


Maintenant essayons de pr??voir les part de march?? de BMW, Audi et Mercedes en fonction des caract??ristiques de leurs voitures

```{r}
predict.mnl <- function(model, data) {
  # Function for predicting shares from a multinomial logit model
  # model: mlogit object returned by mlogit()
  # data: a data frame containing the set of designs for which you want to
  # predict shares. Same format as the data used to estimate model.
  data.model <- model.matrix(update(model$formula, 0 ~ .), data = data)[,-1]
  utility <- data.model %*% model$coef#marix multiplication
  share <- exp(utility)/sum(exp(utility))#convert set back to prob
  cbind(share, data)
}

car0 <- c(brand="BMW", price=15, type="city_car", gear="manual", options="all")
car1 <- c(brand="BMW", price=20, type="SUV", gear="auto", options="some")
car2 <- c(brand="Mercedes", price=15, type="city_car",  gear="manual", options="some")
car3 <- c(brand="Mercedes", price=20, type="Berline",  gear="auto", options="none")
car4 <- c(brand="Audi", price=25, type="Berline",  gear="manual", options="some")
car5 <- c(brand="Audi", price=25, type="SUV",  gear="auto", options="some")
cars <- data.frame(rbind(car0, car1, car2, car3, car4, car5))
cars$price <- as.numeric(as.character(cars$price))

predict.mnl(m1, cars)

# create a grid with all possible design and select the ones we are interested in (in general the ones your company is offering)
#attrib<-list(seat=c("6","7","8"),cargo=c("2ft","3ft"),eng=c("gas","hyb","elec"),price=c("30","35","40"))
#total amount of combinations: 3*2*3*3=54
#(new.data<-expand.grid(attrib)[c(8,1,3,41,49,26),])#randomly pick a few combos as "real" market options
#predict.mnl(m3,new.data)
```

```{r}
sensitivity.mnl <- function(model, attrib, base.data, competitor.data) {
  # Function for creating data for a share-sensitivity chart
  # model: mlogit object returned by mlogit() function
  # attrib: list of vectors with attribute levels to be used in sensitivity
  # base.data: data frame containing baseline design of target product
  # competitor.data: data frame contining design of competitive set
  data <- rbind(base.data, competitor.data)
  base.share <- predict.mnl(model, data)[1,1]
  share <- NULL
  for (a in seq_along(attrib)) {
    for (i in attrib[[a]]) {
      data[1,] <- base.data
      data[1, a] <- i
      share <- c(share, predict.mnl(model, data)[1,1])
    }
  }
  data.frame(level=unlist(attrib), share=share, increase=share-base.share)

}

base.data <- data.frame(rbind(car5))
base.data$price <- as.numeric(as.character(base.data$price))

competitor.data <- data.frame(rbind(car0, car1, car2, car3, car4))
competitor.data$price <- as.numeric(as.character(competitor.data$price))

attrib<-list(brand=c("Audi"), price=levels(x$price), type=c("Berline", "city_car", "SUV"), gear=levels(x$gear), options=levels(x$options))

tradeoff <- sensitivity.mnl(m1, attrib, base.data, competitor.data)

barplot(tradeoff$increase, horiz=FALSE, names.arg=tradeoff$level,
        ylab="Change in Share for Baseline Product")
#shows how share would change if we changed each of the attributes of the design one at a time in comparison to a existing alternative (8)
```




#2. random effect/heterogen mnlogit: each respondent has his own utility coef

```{r}
m1.rpar <- rep("n", length=length(m1$coef))
names(m1.rpar) <- names(m1$coef)
m1.rpar
m1.hier <- mlogit(choice ~ 0 + brand + price + type + gear + options,data = car.mlogit, panel=TRUE, rpar = m1.rpar, correlation = FALSE)
#panel=true means multiple questions per respondent
#assume utilities are not correlated
summary(m1.hier)
stdev(m1.hier)
# a lot of spread for the 8 seat choice: people prefer 6 but there are also a bunch of people going for 8

m2.hier <- update(m1.hier, correlation = TRUE)
summary(m2.hier)
cov2cor(cov.mlogit(m2.hier))
#correlation between levels of seating: normal the respondent thinks it is an important factor when increasing/decreasing

# Simulating shares
predict.hier.mnl <- function(model, data, nresp=1000) {
  # Function for predicting shares from a hierarchical multinomial logit model 
  # model: mlogit object returned by mlogit()
  # data: a data frame containing the set of designs for which you want to 
  #       predict shares.  Same format at the data used to estimate model. 
  # Note that this code assumes all model parameters are random
  data.model <- model.matrix(update(model$formula, 0 ~ .), data = data)[,-1]
  coef.Sigma <- cov.mlogit(model)
  coef.mu <- model$coef[1:dim(coef.Sigma)[1]]
  draws <- mvrnorm(n=nresp, coef.mu, coef.Sigma)
  shares <- matrix(NA, nrow=nresp, ncol=nrow(data))
  for (i in 1:nresp) {
    utility <- data.model%*%draws[i,]
    share = exp(utility)/sum(exp(utility))
    shares[i,] <- share
  }
  cbind(colMeans(shares), data)
}

predict.hier.mnl(m2.hier, data=cars)
```
