---
title: "Customer Intelligence"
author: '[Leonard Henriquez](https://github.com/leonard-henriquez/), [Adrien Lequiller](https://github.com/adrienlequiller) & [Eddy Ohayon](https://github.com/Eddoha55)'
date: "`r Sys.Date()`"
output: html_document
always_allow_html: yes
---

# Data preparation

```{r message=FALSE, warning=FALSE, include=FALSE}
# Options
knitr::opts_chunk$set(cache = TRUE, warning=FALSE)
```

Read in the data

```{r}
# all alternatives
x<-read.csv("input/19019700001_conjoint_choice_dat_X.csv")
#x$Price<-as.factor(as.character(x$Price))
# choice per display group
y<-read.csv("input/19019700001_conjoint_choice_dat_y.csv")
# demographic information
z<-read.csv("input/19019700001_conjoint_choice_dat_Z.csv")
```

Transform the data into long format

```{r}
choicesperquestions<-3

y[1,2]
for (i in 1:nrow(y))
{
  y[i,2]=(i-1)*choicesperquestions+y[i,2]
}

x$response<-0
for (i in 1:nrow(y))
{
  j=y[i,2]
  x[j,8]<-1
}

x$Profile<-NULL
alternative<-1
questioncounter<-1
x$ques<-0
x$alt<-0
lastid<-x[1,1]
for (i in 1:nrow(x))
{
  if(x[i,1]!=lastid)
  {
    lastid=x[i,1]
    questioncounter<-0
  }
  if(alternative<=choicesperquestions)
  {
    x[i,8]<-questioncounter
    x[i,9]<-alternative
    alternative<-alternative+1
  }
  else
  {
    questioncounter<-questioncounter+1
    alternative<-1
    x[i,8]<-questioncounter
    x[i,9]<-alternative
    alternative<-alternative+1
  }
}

# merge a valid covariate here: in my case sex or Q1.
x<-merge(x,z,by="ID",all.x=TRUE)
colnames(x)[10] <- "sex"
colnames(x)[11] <- "perception"
x$Q2.<-NULL
summary(x)
```

Our data x is now in the long format so you can launch the first two solution methods

# Analysis

Use understanding code to make it ready for the third method (Hierarchical Bayes multinomial logit)

```{r}
choice <- rep(0, nrow(x))
choice[x[,"response"]==1] <- x[x[,"response"]==1,"alt"]
```

Indicate which out of the 3 alternatives per question is chosen

```{r}
head(choice)
```

Convert the factor levels to dummies: change the name of factor to your factor names

```{r}
x.coded <- model.matrix(~ Brand + Price + Type + Gear + Options, data = x) # change this to your own factors
x.coded <- x.coded[, -1] # remove the intercept
```

Combine everything back into a df

```{r}
choicemodelr.data <- cbind(x[, 1:3], x.coded, choice)
head(choicemodelr.data)
```

Covariate: change sex into the name of your covariate

```{r}
sex <- x$sex[x$ques==1 & x$alt==1]=="Male "# for each respondent
sex <- as.numeric(sex)
demos <- as.matrix(sex, nrow=length(sex))
```
